US Korea Exchange Rates \\ STA206 Final Project

### 2014-12-14 paper.tex
abstract

\begin{abstract}
    We analyze the exchange rate between the United States and South Korea
    (hereafter Korea) using monthly country level economic data.
\end{abstract}

@@

The outliers can be readily detected in the diagnostic plots 
figure~\ref{fig:cooks}. We see
that the points 113 and 117 are the primary outlying cases, which have
absolute DFFIT values of 1.16 and 0.89. This is much bigger than the cutoff
of $2 / \sqrt{p / n} = 0.445$. Cook's distance is large as well.
Looking up the
corresponding dates reveals that these are the points occuring during
October 2008 and February 2009, during the subprime mortgage crisis
which shook the global economy. There are no points between 113 and 117
because the test train split didn't select them. In the validation set we
discovered similar results for this period(114, 118). The subprime mortgage
crisis is the reason that they are outliers. So, we took off the outliers
from our data set to get model 1 fit~\ref{m1:train}. We also had trouble
with recent dates having large leverage values of around 0.16, which is
greater than the threshold of $2 * p / n = 0.08$.

@@

The model above is difficult to interpret, so we decided to center the data
to minimize multicollinearity and get more accessible numbers. After a
similar analysis process as described above we found that the final model
for the centered data has the same variables as well as \texttt{export}.

common variables and export variable. Interesting part of this trial is
about outliers. Its outliers are showing up 2000 finanical crisis rather
than the subprime mortage crisis (it fitted well)~\ref{centered}.

We used Bonferroni's method to construct simultaneous 95\% confidence intervals
for each of the 5 variables selected in the centered model.

@@

Our use of dynamic data caused trouble because the data was a little too
dynamic.

Our model: $\frac{USA dollar Worthy}{KOREA Won Worthy} \sim \frac{KOREA gdp}{USA GDP} - \frac{KOREA Interest Rate}{USA Interest Rate} -  Korea inflation + USA inflation$, means when relative Korea gdp over US gdp is increasing, the won per a dollar is decreasing. The Korea Interest Rate is relatively increased over the USA Interest rate(higher interest rate means higher liquidity of money in markets), which bring the won per a dollar is increasing. Also, the signs of Korea inflation and USA inflation are different, which is very reliable because we are predicting the $\frac{USA dollar Worthy}{KOREA Won Worthy}$.

Commonly, we can think if you want to exchage your currency to other foriegn currency, it would better off to do it when your country's relative gdp is greater than the foriegn, when your country's relative interest rate is less , when your contry is not on inflation, or when the foriegn country is on inflation situation.
We have noticed exchange rates are dependent on previous exchage rates(time series) if we are available to do mutltivariate time series.

@@

@@

\subsubsection{Bonferroni's confidence intervals on centered coefficients}

\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & lower & upper \\
  \hline
(Intercept) & -0.10 & 0.02 \\
  gdp & -0.80 & -0.57 \\
  exports & -0.37 & -0.13 \\
  interest\_rate & 0.51 & 0.68 \\
  inflation\_KOR & 0.22 & 0.35 \\
  inflation\_USA & -0.37 & -0.22 \\
   \hline
\end{tabular}
\end{table}

>>>>

\begin{abstract}

    We analyze the exchange rate between the United States and South Korea
    (hereafter Korea) using monthly country level economic data and find
    that ratios of economic indicators are useful in confirming economic
    reasoning about the relative strengths of the two national economies.

\end{abstract}

@@

The outliers can be readily detected in the diagnostic plots 
figure~\ref{fig:cooks}. We see
that the points 113 and 117 are the primary outlying cases, which have
absolute DFFIT values of 1.16 and 0.89. This is much bigger than the cutoff
of $2 \sqrt{p / n} = 0.445$. Cook's distance is large as well.
Looking up the
corresponding dates reveals that these are the points occuring during
October 2008 and February 2009, during the subprime mortgage crisis
which shook the global economy. There are no points between 113 and 117
because the test train split didn't select them. In the validation set we
discovered similar results for this period(114, 118). The subprime mortgage
crisis is the reason that they are outliers. So, we took off the outliers
from our data set to get model 1 fit~\ref{m1:train}. We also had trouble
with recent dates having large leverage values of around 0.16, which is
greater than the threshold of $2 * p / n = 0.08$.

@@

The model above is difficult to interpret, so we decided to center the data
to minimize multicollinearity and instead focus on the sign of the
coefficients. After a
similar analysis process we found that the final model
for the centered data has the same variables as well as \texttt{exports}.
The interesting part here were again the outliers, which this time also included
a point from the 2000 financial crisis (see \ref{centered} in the appendix). This fit came out
quite well, and the corresponding diagnostic plots can be seen in 
Figure \ref{fig:final_residual}.

We used Bonferroni's method to construct simultaneous 95\% confidence intervals
for each of the 5 variables selected in the centered model, producing the
following intervals:

\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & lower & upper \\
  \hline
  gdp & -0.80 & -0.57 \\
  exports & -0.37 & -0.13 \\
  interest\_rate & 0.51 & 0.68 \\
  inflation\_KOR & 0.22 & 0.35 \\
  inflation\_USA & -0.37 & -0.22 \\
   \hline
\end{tabular}
\end{table}

@@

Let $Y$ be the exchange rate of Korean Won per US Dollar. Let $G, E, R, I$
represent the value of GDP, exports, interest rate, and inflation, respectively.
Let $X_K$ be the values for Korea and $X_{US}$ be the ones for the US. Let
$c_i$ be a nonnegative scalar for scaling.
The final model becomes

\[
    Y = -0.69 c_1 \frac{G_{K}}{G_{US}}
    -0.25 c_2 \frac{E_{K}}{E_{US}}
    +0.59 c_3 \frac{R_{K}}{R_{US}}
    +0.29 c_4I_{K} - 0.30 c_5 I_{US} + \epsilon.
\]

The 95\% confidence interval does not include 0 for any of these variables,
so we are 95\% confident that these signs are correct. Since the predictor variables
are scaled or ratios they are unitless. Now the model has a
natural interpretation. Suppose that the Korean economy grows while the US
economy remains stagnant. Then the exchange rate should decrease, because
the Korean Won will have more value relative to the US Dollar.
From our model we can infer the following:

\begin{enumerate}
    \item The negative coefficient of $\frac{G_{K}}{G_{US}}$ means that as
        the GDP of Korea increases relative to that of the US, the exchange
        rate decreases. 
    \item The negative coefficient of $\frac{E_{K}}{E_{US}}$ means that if
        Korea increases its exports relative to the US, the exchange rate
        decreases.
    \item The positive coefficient of $I_K$ means that the exchange rate
        increases as the inflation in Korea gets larger. This is a direct
        relation that we would expect.
    \item The negative coefficient of $I_{US}$ means that the exchange rate
        decreases as the inflation in the US gets larger.
\end{enumerate}

Common sense and economic reasoning tells us that all of these should be
true. The data and analysis confirm our intuition. Perhaps with the use of
time series techniques this analysis could be extended.

Returning to out original questions, the results of this analysis suggest
that if you want to exchange your currency
to foreign currency, it would be better to do it when your home country's 
GDP is good, or the exports are good, or the inflation is relatively lower.

@@

\begin{figure}
  \centering
    \includegraphics{final_residual.pdf}
  \caption{final residual plots for centered model}
  \label{fig:final_residual}
\end{figure}

@@
